Theoretical prediction of disrupted Min oscillation in flattened \emph{Escherichia coli}

### 2015-06-08 paper/plos.tex
remove acknowledgements content. Tested everything on bennet.
add outline of comments from referees Tested everything on bennet.

@@

% Do NOT remove this, even if you are not including acknowledgments.
\section*{Acknowledgments}
Cras egestas velit mauris, eu mollis turpis pellentesque sit
amet. Interdum et malesuada fames ac ante ipsum primis in
faucibus. Nam id pretium nisi. Sed ac quam id nisi malesuada
congue. Sed interdum aliquet augue, at pellentesque quam rhoncus
vitae.

>>>>

{
  \color{red}
  Referee 1.
  \begin{enumerate}
  \item Need to better justify use of Huang.
  \item Couldn't another deterministic model predict Mannik's results?
  \item The stadia seem on average to be symmetric.
  \item MINOR:
  \item New citation for earlier observation.
  \item A couple of clarifications of our descriptions of cited papers.
  \item Stochastic are also important for a PNAS 2010 work.
  \end{enumerate}

  Referee 3
  \begin{enumerate}
  \item Skepticism about the effect of flattening, in terms of
    coherence times in particular.
  \item Want more clarity with regard to how we divide up the cell to
    compute coherence times.
  \item Starry night patterns are inconsistent with experimetns.
    Membrane diffusion may alleviate this problem.
  \item MINOR:
  \item Clarification in caption.  I don't quite understand.
  \item Figure 2 units for colormap.
  \item Figure 4 caption needs some title for the figure, not just
    ``We display here...''.
  \item ``coli'' should not be capitalized.
  \item FtsZ polymer does not form on the cell wall but near the
    cytoplasmic side of the inner membrane.
  \end{enumerate}
}

@@

% Do NOT remove this, even if you are not including acknowledgments.
\section*{Acknowledgments}
